### 2018-05-01 paper/related.tex

Mixnets~\cite{Chaum:1981} are perhaps the first solution to turn to for sending content from A to B anonymously. In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching. We thus decided for an approach based on onion routing.

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

>>>>

Mixnets~\cite{Chaum:1981} are perhaps the first solution to turn to for sending content from A to B anonymously. In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching. We thus decided for an approach based on onion routing, which also entails sender-receiver anonymity.

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{Clarke:2001}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

### 2018-05-01 paper/squad-overlay-design.tex

At the root of \name is predictive routing, based on the concept of Probabilistic Onion Routes (POR).
To create PORs, as a device's availability strongly depends on the activity of its owner,
 a user's devices (her \squad) must predict the future behavior of their owner. 
However, one device, belonging to an \squad, can only predict its probability to stay online in the near future
if it has a global knowledge of the user behavior over the other devices of the \squad it belongs to.
To reach this aim, \name relies on a \squad overlay to share the user's behavior among devices of its \squad.

@@

%Online devices want to know whether they are likely to stay online in the near future.
taken separately, each device only knows local information such as when its user used it, and potentially mobility information if it is handheld device. When combining all these local observations, each device can obtain a refined model of the user’s behavior to predict its future activity in an accurate manner. To build this sequence of observations, 
%a sequence of the user's behavior that is far more complete.
%For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
the \squad overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
it allows one's devices to inform one another every time the user performs an action.
In our previous work~\cite{luxey:cascade}, we showed that \textsc{Sprinkler} is resilient to devices churn: 
devices let each other know of what they have missed while offline.
We thus employ \textsc{Sprinkler} to disseminate the user's activity to its \squad.

@@

we need a probabilistic model of the user's behavior to predict its future activity.
In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
In our model, time is discretized, i.e. users periodically change the availability stated of their devices in a predefined period.
We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
Our goal is to predict $O_{t+1}$ knowing $O_t$.

@@

Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.

>>>>

At the root of \name is predictive routing, based on the concept of Probabilistic Onion Routes (POR).
To create PORs, as a device's availability strongly depends on the activity of its owner,
 a user's devices (her \squad) must predict the future behavior of their owner. 
However, one device, belonging to an \squad, can only predict its probability to stay online in the near future
if it has a global knowledge of the user behavior over the other devices of the \squad it belongs to.
To reach this aim, \name relies on a overlay, named thereafter the \squad overlay, to share the user's behavior among devices of its \squad.

@@

%Online devices want to know whether they are likely to stay online in the near future.
taken separately, each device can only get local observations, such as when its user used it, and mobility information if it is a handheld device.
If all these local observations can be combined, a device can infer a refined model of the user’s behavior to predict its future activity in an accurate manner. To build such a sequence of observations, 
%a sequence of the user's behavior that is far more complete.
%For instance, the probability that Alice uses her home computer and workstation simultaneously is null: these devices are too far apart.
the \squad overlay leverages on a probabilistic dissemination protocol, \textsc{Sprinkler}~\cite{luxey:hal-01704172}.
it allows one's devices to inform one another every time the user performs an action.
In our previous work~\cite{luxey:cascade}, we showed that \textsc{Sprinkler} is resilient to devices churn: 
devices let each other know of what they have missed while offline.
We thus employ \textsc{Sprinkler} to disseminate the user's activity to its \squad.

@@

we need a probabilistic model of the user's behavior to predict its future activity.
In \name, the only data we collect and share, through the \squad overlay, are the availability times of each device among a \squad.
In our model, time is discretized, i.e. users periodically change the state availability of their devices in a predefined period.
We store the availability times in an ever-increasing \emph{sequence} $O=O_1, ..., O_i, ...$ of actions performed at every \emph{round}, that lasts a short period of time $T$. 
$d \in O_t$ thus means that the device $d$ was online from time $t$ to time $t+T$.
Our goal is to predict $O_{t+1}$ knowing $O_t$.

@@

Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
%This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.

### 2018-05-01 paper/system-model.tex

\name is a distributed system made of users' devices. 
Each device can communicate with any other device that it knows the
address for (\eg using the Internet). All devices belonging to one user
 know which other devices belong to the same user, \ie the \squad.
Thus the devices from an \squad only knows the mapping from devices to users for the devices in 
the \squad it belongs to.
We also assume that the users can exchange some limited amounts of data 
out-of-band, \ie through some other channel than the network just mentioned (\eg 
using \ac{NFC}).

@@

\paragraph*{In the \name setting} when changing from the cloud setting
to \ac{P2P}, we want to keep the privacy that Alice and Bob already
enjoyed through the cloud provider, and go a step further by removing 
cloud provider that may act as a spy. However, this increased privacy
should not be done to the benefit of the user's friends that may
become the most powerful potential attackers, and act
as an adversary type of friends.
In this context, in \name, we want to protect users from friendly
surveillance~\cite{FriendlySurveillance} in an honest-but-curious setting.

>>>>

\name is a distributed system made of users' devices. 
Each device can communicate with any other device that it knows the
address for (\eg using the Internet). All devices belonging to one user
 know which other devices belong to the same user, \ie the \squad.
Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
the \squad they belong to.
We also assume that users can exchange some limited amounts of data 
out-of-band, \ie through some other channel than the network just mentioned (\eg 
using \ac{NFC}).

@@

\paragraph*{In the \name setting} when changing from the cloud setting
to \ac{P2P}, we want to keep the privacy that Alice and Bob already
enjoyed through the cloud provider, and go a step further by removing 
the cloud provider that may act as a spy. However, this increased privacy
should not be done to the benefit of the user's friends that may
become the most powerful potential attackers, and act
as an adversary type of friends.
In this context, in \name, we want to protect users from friendly
surveillance~\cite{FriendlySurveillance} in an honest-but-curious setting.
